### 2023-02-13 article.tex
No supmat in book chapter

Genetic epidemiology is a field within biology that
tries to determine the spread of heritable traits 
and their underlying biological mechanism.
For example, we know that lactose intolerance in adults is
caused by a decline in the production of lactose-degrading enzymes,
and is most commonly found in south-east Asia and south Africa \cite{storhaug2017country}.
The trait is caused by the genetic make-up, or 'genotype'
(see Table \ref{tab:definitions} in the Supplementary Materials
for the definitions of terms used in this paper), of a person.
The trait, also called 'phenotype', 
in this example is lactose intolerance at adult age,
yet any human property, such as weight or height can be studied.
When an association between genotype and phenotype is found,
these associations, when relevant enough, are used to 
create so-called 'gene panels', 
where the location of the gene causing 
an association is measured specifically, 
to detect people at risk for the associated phenotype.
The rest of this section describes a genetic epidemiology study 
in more detail, with special focus on the computational experiment.

@@

@@

\iffalse
\begin{table}[h]
  \begin{tabular}{|p{2cm}|l|}
    \hline
    \textbf{Type of code} & \textbf{Recommendation} \\
    \hline
    No code       & Disallow papers that do not supply code publicly \\
    \hline
    Raw code      & Don't publish raw code as text, host it on a code hosting website \\
    \hline
    Hosted code   & Use a standarized badge for build status \\
                  & Use a standarized badge for code coverage \\
                  & Standardize to link between paper and code host \\
    \hline
    Runnable code & Allow to upload containers without limits \\
                  & Website to host containers must allow for annotation \\
                  & Use a standarized badge for the container to be functioning  \\
                  & Standarize to link between container, paper and code repository \\
    \hline
  \end{tabular}
  \caption{Recommendations described in this paper}
  \label{tab:recommendations}
\end{table}
\fi

>>>>

Genetic epidemiology is a field within biology that
tries to determine the spread of heritable traits 
and their underlying biological mechanism.
For example, we know that lactose intolerance in adults is
caused by a decline in the production of lactose-degrading enzymes,
and is most commonly found in south-east Asia and south Africa \cite{storhaug2017country}.
The trait is caused by the genetic make-up, or 'genotype'
\iffalse
(see Table \ref{tab:definitions} in the Supplementary Materials
for the definitions of terms used in this paper)
\fi
, of a person.
The trait, also called 'phenotype', 
in this example is lactose intolerance at adult age,
yet any human property, such as weight or height can be studied.
When an association between genotype and phenotype is found,
these associations, when relevant enough, are used to 
create so-called 'gene panels', 
where the location of the gene causing 
an association is measured specifically, 
to detect people at risk for the associated phenotype.
The rest of this section describes a genetic epidemiology study 
in more detail, with special focus on the computational experiment.

@@

\iffalse

@@

\begin{table}[h]
  \begin{tabular}{|p{2cm}|l|}
    \hline
    \textbf{Type of code} & \textbf{Recommendation} \\
    \hline
    No code       & Disallow papers that do not supply code publicly \\
    \hline
    Raw code      & Don't publish raw code as text, host it on a code hosting website \\
    \hline
    Hosted code   & Use a standarized badge for build status \\
                  & Use a standarized badge for code coverage \\
                  & Standardize to link between paper and code host \\
    \hline
    Runnable code & Allow to upload containers without limits \\
                  & Website to host containers must allow for annotation \\
                  & Use a standarized badge for the container to be functioning  \\
                  & Standarize to link between container, paper and code repository \\
    \hline
  \end{tabular}
  \caption{Recommendations described in this paper}
  \label{tab:recommendations}
\end{table}

\fi
